\documentclass{article}
\linespread{2.0}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{systeme}
\usepackage{graphicx} % Required for inserting images

\begin{document}
Find a power series, or disprove, such that:

\begin{enumerate}
\item Converges for all values $x\in\mathbb{R}$.
\item Diverges for all values $x\in\mathbb{R}$.
\item Converges absolutely for all $x\in[-1,1]$ and diverges otherwise.
\item Converges conditionally at $x=-1$ and converges absolutely at $x=1$
\item Converges conditionally at both $x=-1$ and $x=1$.
\end{enumerate}

Proof:

\begin{enumerate}
    \item Yes. Let $a_i = 0$. Then $a_ix^i = 0$ for all $x \in \mathbb{R}$, so the series converges.
    
    \item No. Let $x = 0$. Then $a_ix^i = 0$ for all $i$, so the series converges.
    
    \item Yes. Let $a_n = \frac{1}{n^2}$. For $x=\pm 1$, the series becomes $\sum |\frac{1}{n^2}| = \sum \frac{1}{n^2}$, which is absolutely convergent. Since the power series converges at $x=1$, it converges absolutely on $(-1,1)$, therefore on $[-1,1]$ (Theorem $6.5.1$.)
    
    For $x > 1$, let $x = 1 + \epsilon$ for some $\epsilon > 0$. Since, as $n \to \infty$, $\sqrt[n]{n} \to 1$, there exists $N \in \mathbb{N}$ such that for any $n \geq N$, $1+\epsilon > \sqrt[n]{n}$, and the series becomes $\sum a_nx^n = \sum \frac{(1+\epsilon)^n}{n^2} > \sum \frac{n}{n^2} = \sum \frac{1}{n}$. So by Comparison Test, it diverges.

    For $x < -1$, let $x = -(1+\epsilon)$ for some $\epsilon > 0$. The series becomes $\sum a_nx^n = \sum \frac{(-1-\epsilon)^n}{n^2} > \sum \frac{-n}{n^2} > \sum \frac{-1}{n}$. So by Comparison Test, it diverges.
    
    \item No. Since the series converges absolutely at $x=1$, the series \\$\sum |a_n|$ converges. Since the series converges conditionally at $x=-1$, the series $\sum|a_n(-1)^n| = \sum|a_n|$ diverges, which is contradictory.
    \item Yes. Let $x_0 = 0$. For $n \geq 1$, let \[a_n = \begin{cases}0 & n \textit{ is odd} \\ \frac{(-1)^{\frac{n}{2}+1}}{\frac{n}{2}}& n \textit{ is even}\end{cases}\]. 
    
    At $x= \pm1$, the series becomes $\sum a_nx^n = a_2+a_4+a_6 + \dots =  1 - \frac{1}{2} + \frac{1}{3} - \frac{1}{4} + \dots$, which converges conditionally.
\end{enumerate}
$\square$
\end{document}
